\cvsection{Experience}

\begin{cventries}
    \cventry
    {Human-Robot Interaction Laboratory \textemdash University of New Brunswick}
    {\textbf{RESEARCH ASSISTANT}}
    {UNB, Fredericton, Canada}
    {September 2023 - Present (2 years)}
    {
        \begin{itemize}
            \item Built teleoperation interfaces with ROS + Python (Tkinter); implemented an MVC architecture to improve reliability and developer velocity.
            \item Investigated connectivity and networking issues (routing, DNS, ROS master) and implemented automated recovery routines to stabilize robot communication.
            \item Performed hardware diagnostics on the Jackal’s MCU/User Power Board—re-terminating connectors, verifying VBAT/power continuity, and preventing intermittent disconnections.
            \item Maintained and refactored a legacy codebase, improving readability, modularity, and documentation quality.
            \item Contributed to ongoing research on UI/UX design, system robustness, and human-robot interaction for teleoperation studies. (Empathy with Teleoperated Robots, and Mitigating Racial and Gender Bias Using Avatar Robots)
            % \item Worked with Python TKinter, ROS, ShellScripts
        \end{itemize}}
    \vspace{0.4 cm}
\end{cventries}

% \begin{cventries}
%     \cventry
%     {Algorithms Design and Analysis}
%     {\textbf{TEACHING ASSISTANT}}
%     {UNB, Fredericton, Canada}
%     {Winter 2025}
%     {
%         \begin{itemize}
%             \item Instructor: Huajie Zhang; Responsible for marking and reviewing assignments
%         \end{itemize}
%     }
%     \vspace{0.4 cm}
% \end{cventries}

% \begin{cventries}
%     \cventry
%     {Introduction to Game Development}
%     {\textbf{TEACHING ASSISTANT}}
%     {UNB, Fredericton, Canada}
%     {Winter 2024}
%     {
%         \begin{itemize}
%             \item Instructor: Daniel Rea; Responsible for marking and reviewing assignments, as well as tutorial outline
%             \item Worked with Godot Engine.
%         \end{itemize}
%     }
%     \vspace{0.4 cm}
% \end{cventries}

% \begin{cventries}
%     \cventry
%     {\textbf{RESEARCH ASSOCIATE}}
%     {Human-Robot Interaction Laboratory}
%     {UNB, Fredericton, Canada}
%     {May - September 2024}
%     {Technical Lead, co-author, designer, and conductor of the studies of underlying unconscious biases through interactions via avatars and teleoperated robots, in a professional setting.
%     }
%     \vspace{0.4 cm}
% \end{cventries}

\begin{cventries}
    \cventry
    {Robotics Laboratory \textemdash Shahid Beheshti University}
    {\textbf{RESEARCH ASSISTANT}}
    {SBU, Tehran, Iran}
    {July 2021 - October 2023 (2 years 3 months)}
    {
        \begin{itemize}
            \item Explored and evaluated reinforcement-learning methods (DQN, PPO) andevolutionary algorithms, integrating them with PyTorch and Python modules, and linking via Redis-based local networking and sensor data exchange. This work aimed to improve the value-function estimation in our existing chain-action module for RCSS2D intelligent agents.
            \item  Worked with C++, Pandas, TensorFlow, PyTorch, ROS, Webots, and Docker
        \end{itemize}
    }
    \vspace{0.4 cm}
\end{cventries}

\begin{cventries}
    \cventry
    {Robotics Laboratory \textemdash Shahid Beheshti University}
    {\textbf{TEAM LEAD}}
    {SBU, Tehran, Iran}
    {September 2021 - August 2023 (2 years)}
    {
        \begin{itemize}
            \item Coordinated lab ongoing projects, onboarding, and weekly meetings across 9 active members.
            \item Secured a sponsorship grant from Divar to support competition and lab activities.
            \item Managed Git and version control, set branching strategies, code reviews, andreleases.
            \item Designed and operationalized technical frameworks, establishing workflows, roles, processes, and milestones for four different projects (RoboCup 2dsim, Quadcopter drone, SBU Robot, and NAO).
            \item Packaged modules for the intelligent systems' fit, and majorly responsible for integration to the code base.
            \item Ran statistical analyses to assess quality of new developments; built a semi-manual CI/CD-style validation pipeline with in-house tools, and parsed/processed sparse datasets across projects to produce actionable QA reports.
        \end{itemize}
    }
\end{cventries}

\begin{cventries}
    \cventry
    {Robotics Laboratory \textemdash Shahid Beheshti University}
    {\textbf{ROBOTICS ENGINEER INTERN}}
    {SBU, Tehran, Iran}
    {May 2021 - September 2021 (5 months)}
    {
        \begin{itemize}
            \item Implemented and evaluated bug algorithms and obstacle-avoidance (Webots, Python); later explored particle filters and SLAM for higher autonomy (Webots, ROS, Python).
            \item Improved sonar-based obstacle detection (corner-miss issue) via semi-circular sweep motion; compared against sensor-swap and decoupled-panel alternatives for accuracy and energy.
            \item Set up ROS 2 platform and packages; worked with networking, nodes, and launch configs.
            \item Fixed Webots 3D model issues (URDF/PROTO) on the SBU omni-directional robot to resolve dynamic-motion failures.
        \end{itemize}
    }
\end{cventries}

\begin{cventries}
    \cventry
    {Concealand Game Studio}
    {\textbf{GAME DEVELOPER INTERN}}
    {Tehran, Iran}
    {January - August 2023}
    {
        \begin{itemize}    
            \item Applied Reinforcement Learning, Imitation Learning, and Curriculum Learning for Procedural Animation of a humanoid character to reduce the animation state complexity and workload for artists.
            \item Worked with Unity IK frameworks, animation rigging package, and ML model training
        \end{itemize}
    }
\end{cventries}


% \vspace{0.4 cm}
%\cvsection{Internship}
% \begin{cventries}
%     \cventry
%     {Introduction to Algorithms Design}
%     {\textbf{TEACHING ASSISTANT}}
%     {Shahid Beheshti University, Tehran, Iran}
%     {September - December 2022}
%     {
%         \begin{itemize}
%             \item Instructor: Ramak Ghavamizadeh; Responsible for teaching labs and designing lab assignment problemsets.
%             \item Used C++ and bash scripts to automate the test units for marking while assessing edge cases in each problem.
%         \end{itemize}
%     }
%     \vspace{0.4 cm}
% \end{cventries}

% \begin{cventries}
%     \cventry
%     {Digital Logic Circuits}
%     {\textbf{TEACHING ASSISTANT}}
%     {Shahid Beheshti University, Tehran, Iran}
%     {September 2022 - December 2022}
%     {
%         \begin{itemize}
%             \item Instructor: Ramak Ghavamizadeh; Responsible for marking labs and assignments.
%         \end{itemize}
%     }
%     \vspace{0.4 cm}
% \end{cventries}

% \begin{cventries}
%     \cventry
%     {Introduction to Robotics}
%     {\textbf{INSTRUCTOR}}
%     {SBU, Tehran, Iran}
%     {June - September 2022}
%     {Instructed for summer workshops, in order to recruit new passionate individuals for the lab.
%     \newline Taught Fundamentals of Robotics, Machine Learning, A.I. Algorithms, and Simulation concepts, using C++ and Python}
%     \vspace{0.4 cm}
% \end{cventries}

% \begin{cventries}
%     \cventry
%     {Introduction to Robotics}
%     {\textbf{INSTRUCTOR}}
%     {SBU, Tehran, Iran}
%     {June - August 2023
%      June - August 2022}
%     {
%         \begin{itemize}
%             \item Instructed for summer workshops for undergraduate students and lab recruitment.
%             \item Taught Fundamentals of Robotics, Machine Learning, A.I. Algorithms, and Simulation concepts, Using Python and C++
%         \end{itemize}
%     }
%     \vspace{0.4 cm}
% \end{cventries}